Structural controllability of ecological networks

### 2018-06-30 paper/manuscript.Rmd
Minor mistakes corrected

Our choice of studying invaded/uninvaded networks was based on a desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
Without exception, we found that invasive plants were critical for network control and as such our results were in line with our expectations. 
Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016]. 
We found that invasive plants are, however, unlikely to be inherently different from their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
Just like any other mutualist in our dataset, invasive plants tended to attain a high control capacity proportional to the degree to which they contribute to network persistence, are abundant, and depend little on other species. 
Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities\R{extra-references-3} [@kaiser-bunbury_ecosystem_2017]. 
However, our results also suggest that removals must be exercised with caution. 
Not only it is hard to predict the direction in which the system will change, but we also show that critical species can underpin the coexistence of species and therefore some communities may be acutely vulnerable to their eradication [@traveset_invaders_2013; @albrecht_consequences_2014].

>>>>

Our choice of studying invaded/uninvaded networks was based on a desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
Without exception, we found that invasive plants were critical for network control and as such our results were in line with our expectations. 
Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016]. 
We found that invasive plants are, however, unlikely to be inherently different from their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
Just like any other mutualist in our dataset, invasive plants tended to attain a high control capacity proportional to the degree to which they contribute to network persistence, are abundant, and depend little on other species. 
Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities\R{extra-references-3} [@kaiser-bunbury_ecosystem_2017]. 
However, our results also suggest that removals must be exercised with caution. 
Not only it is hard to predict the direction in which the system will change, but we also show that critical species can underpin the coexistence of species and therefore some communities may be acutely vulnerable to their eradication [@traveset_invaders_2013; @albrecht_consequences_2014].
